TBD

### 2020-11-02 outputs/paper/paper.Rmd
packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
```

@@

That is

We fit the logistic regressions for estimating candidate support in each cell. We used `function` from `package` to fit \@ref(eq:model).

@@

```{r}
fit <- brms::brm(
  binary ~ (1 | age) + (1 | education) + (1 | race_ethnicity0)+ (1 | hispanic)
  + (1 | household_income) + (1 | state) + (1 | extra_covid_worn_mask),
  family = bernoulli(link = "logit"),
  data = clean_survey
)
print(fit)
```

```{r, eval=FALSE}
# to get the estimated proportions and associated 95% PIs by state
res_state <- fit %>%
  add_predicted_draws(newdata=state_prop %>% 
                        filter(age_group>20, age_group<80, decade_married>1969),
                      allow_new_levels=TRUE) %>%
  rename(kept_name_predict = .prediction) %>% 
  mutate(kept_name_predict_prop = kept_name_predict*prop) %>% 
  group_by(state_name, .draw) %>% 
  summarise(kept_name_predict = sum(kept_name_predict_prop)) %>% 
  group_by(state_name) %>% 
  summarise(mean = mean(kept_name_predict), 
            lower = quantile(kept_name_predict, 0.025), 
            upper = quantile(kept_name_predict, 0.975))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(lme4)
library(rstanarm)
library(brms)
```

@@

That is 30,697,920 cells in total. We fit the logistic regressions for estimating candidate support in each cell. We used `function` from `package` to fit \@ref(eq:model).

@@

```{r}
attach(clean_survey)
mod <- brm(binary ~ age + education_grouped + race_ethnicity + hispanic + household_income_grouped + state + extra_covid_worn_mask,
           data = clean_survey,
           family = bernoulli(),
           iter = 4000
           )

summary(mod)
```

```{r}
usa_00001$estimate <-
  mod %>%
  predict(newdata = usa_00001)
```

```{r}
# to get the estimated proportions and associated 95% PIs by state
res_state <- mod %>%
  tidybayes::add_predicted_draws(newdata = census_data) %>%
  rename(president_predict = .prediction) %>%  
  mutate(president_predict_prop = president_predict*prop) %>% 
  group_by(state_name, .draw) %>% 
  summarise(kept_name_predict = sum(kept_name_predict_prop)) %>% 
  group_by(state_name) %>% 
  summarise(mean = mean(kept_name_predict), 
            lower = quantile(kept_name_predict, 0.025), 
            upper = quantile(kept_name_predict, 0.975))
```
